Effect of quality-adjusted production function inputs

### 2015-06-16 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
New section comparing Marco and Calvin CES models.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Marco/Matt coefficient comparison}
\label{sec:marco_matt_coeff_comp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<Comparison, echo=TRUE>>=
# Marco's coefficients for PT, CES, unadjusted, without energy
gamma_marco <- 1.0306
lambda_marco <- 0.0055
delta_1_marco <- 0.9844
rho_1_marco <- 3.4647

# Generate a predicted GDP from a CES model with the above parameters
form <- formulas$PT$unadjusted
form <- keep_summands(form, n = -3) # Remove energy
form
y_hat_marco <- cesCalc(xNames = c(summands(form, n=1), summands(form, n=2)), 
                       data = historicalData$PT, 
                       coef = c(gamma=gamma_marco,
                                lambda=lambda_marco,
                                delta=delta_1_marco,
                                rho=rho_1_marco),
                       tName = summands(form, n=3))
sse_marco <- sum((historicalData$PT$iGDP - y_hat_marco)^2, na.rm=TRUE)
sse_marco # Marco reported 0.6625

# Now do the same thing with Matt's parameters
y <- historicalData$PT$iGDP
coeffs_matt <- naturalCoef(models$PT$unadjusted$noE$CES$kl) 
coeffs_matt
y_hat_matt <- cesCalc(xNames = c(summands(form, n=1), summands(form, n=2)), 
                      data = historicalData$PT, 
                      coef = c(gamma=coeffs_matt$gamma,
                               lambda=coeffs_matt$lambda,
                               delta=coeffs_matt$delta_1,
                               rho=coeffs_matt$rho_1),
                      tName = summands(form, n=3))
sse_matt <- sum((y - y_hat_matt)^2, na.rm=TRUE)
sse_matt

# Get the SSE from the model itself. This is in log space.
r <- resid(models$PT$unadjusted$noE$CES$kl)
sse_matt_log <- sum(r^2)
sse_matt_log # Isn't what we want.

# Convert to linear space
y <- y[!is.na(y)] # removes NA values at end of time series
y_hat <- y / exp(resid(models$PT$unadjusted$noE$CES$kl))
sse_matt_lin <- sum((y - y_hat)^2)
sse_matt_lin
@
